Nesta attacks study

### 2021-08-23 paperDraft/paperDraft.tex
typos fixed, changes implemented suggested by Rafal, webpages bibliography changed

Although much effort has been made in order to tackle the problem of
verbal aggression and harassment online, looking at various reports and
surveys, it remains a common hindrance for people engaging with social
media in their everyday lives. The situation got exacerbated amidst the
COVID19 pandemic, during which a majority of our social life moved to
cyberspace. During this shift, there was an increase in cyberbullying
attitudes and perpetration (Barlett, Simmers, Roth, \& Gentile (2021)),
90\% increase in public reports of illegal online
content\footnote{\href {https://www.aspistrategist.org.au/australias-esafety-commissioner-targets-abuse-online-as-covid-19-supercharges-cyberbullying/}{https://www.aspistrategist.org.au/australias-esafety-commissioner-targets-abuse-online-as-covid-19-supercharges-cyberbullying/}},
including 114\% increase in non-consensual sharing of intimate images,
30\% increase in cyberbullying, as well as 40\% of increase in adults
reporting online harassment. According to a report conducted by company
L1ght \textbackslash footnote\{\textbackslash href
\{\url{https://l1ght.com/Toxicity_during_coronavirus_Report-L1ght.pdf}\}\{\url{https://l1ght.com/Toxicity_during_coronavirus_Report-L1ght.pdf}\}\},
hate speech directed towards China and the Chinese went up by 900\% on
Twitter. Gaming platforms were in the spotlight as well, with a 40\%
increase in toxicity on Discord.

But alongside the growing need for even more efficient and proactive
moderation, the capacity to execute it did not go hand in hand, forcing
companies and policymakers to rethink the current model of moderation
processes and workforce. Due to the COVID19 restrictions including
social distancing, a lot of those serving the role of moderators had to
be sent
home\footnote{\href {https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}{https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}}
without the ability to work remotely because of the constraints
affiliated with restrictive non-disclosure agreements (NDA) among
others. Curtailing the moderators' workforce was accompanied by more
agency given to algorithms and AI-based moderation. Those changes, as
argued by Gerrard (2020), can be seen as a serious red flag in terms of
safety for all users on online platforms.

@@

The hindrances and threats that go along with the Artificial
Intelligence-based methods for moderation have been widely debated, with
the most critical discussions revolving around technology performance
(MacAvaney et al. (2019), Schmidt \& Wiegand (2017)). State-of-the-art
solutions are mostly governed by statistical methods including deep
learning and machine learning (LeCun, Bengio, \& Hinton (2015),
Sejnowski (2020), Jordan \& Mitchell (2015)). Their performance is
inherently tied to the amount of data being fed to the system and the
quality of its annotation. At different stages of the process, from
datasets gathering and preparation, annotation to the training or
algorithms themselves, biases seem to be omnipresent (Binns, Veale, Van
Kleek, \& Shadbolt (2017), Geva, Goldberg, \& Berant (2019) Mehrabi,
Morstatter, Saxena, Lerman, \& Galstyan (2021)). Users' of online
services are also creative in their strategies to circumvent automated
content moderation systems and as shown by Gröndahl, Pajola, Juuti,
Conti, \& Asokan (2018), current techniques are vulnerable to the most
common evasion attacks like word changes (inseting typos and leetspeak),
word-boundary changes (inserting or removing whitespace), or word
appending (appending common or non-hateful words like ``love''). Lack of
generalisability of the models - an ability to perform well on datasets
coming from sources other than the one used for training is a serious
shortcoming as well (Yin \& Zubiaga (2021), Swamy, Jamatia, \& Gambäck
(2019), Rosa et al. (2019)). As shown by Wu, Ribeiro, Heer, \& Weld
(2019), Lipton \& Steinhardt (2019), and Musgrave, Belongie, \& Lim
(2020) in practice, creations of models often lacks thorough error
analysis and legitimate experimental methodology, which can result in
non-reproducibility. This is also connected with a potential lack of
thorough understanding of the limitations of the models and spurious
conclusions being made to a wider public. Specifically, @Lipton \&
Steinhardt (2019) distinguishes four dysfunctional patterns occurring in
the current research paradigm in the industry and academia alike. First,
the inability to draw a clear distinction between speculation and
explanation, with the first one often being disguised as the second.
Second, inability for successful identification of the sources of
empirical gains (whether it was problem formulation, optimization of the
heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet
another aspect). Third, ``mathiness'' - the use obscure language and
often covering weak argumentation with the alluring but often apparent
depth of technical jargon. Last but not least - misuse of language. This
includes suggestive definitions without proper explanation of what they
mean in the context (e.g.~inflating good performance in simple NLP tasks
to human-level understanding), overloading the papers with technical
terminology, or suitcase words (those words that can encompass a variety
of meanings, e.g.~consciousness).

Yet another obstacle in the process is the lack of gold standard in
dataset creation and taxonomies of abusive language being used for
instance in the process of annotating different datasets. Frequently
people obtain data from various sources and do not follow any
universally used instructions when it comes to its annotation, leading
to discrepancies between various datasets being tagged within one domain
(e.g.~hate speech). Lack of expert annotators and proper annotation
criteria and instructions are also widespread, with the common practice
hiring untrained workers from Mechanical Turk or other crowdsourcing
platforms.

Although there are some initiatives developed in response, most notably,
functional tests for Hate Speech Detection Models created by Röttger et
al. (2020), or the Online Safety Data Initiative (OSDI) LINK
\url{https://onlinesafetydata.blog.gov.uk/about-us/}, focused on
projects related to improving access to data, standardizing the
description of online harms, as well as creating tools and benchmarks
for evaluation of technologies focused on safety, much effort must be
made before wider adoption of such solutions comes into force.

At the same time, only automated methods can scan through the massive
amount of content being generated every day on different platforms. On
Facebook, there are more than 3B comments and likes daily
(\url{https://martech.org/facebook-3-2-billion-likes-comments-every-day/}),
500M tweets are sent daily on Twitter
(\url{https://www.oberlo.com/blog/twitter-statistics}), and over 2B
comments made by users of Reddit in 2020
(\url{https://old.reddit.com/r/blog/comments/k967mm/reddit_in_2020/})
which is almost 3M comments made daily. With this amount of content,
it's either impossible or extremely costly to scale the moderation
workforce. One can also have doubts about the ethical aspects of hiring
workers who are often unaware of how this kind of task will affect their
well-being. Being submersed in the cyber-Augean stables takes a toll on
many - as examined by Roberts (2014) \& Roberts (2016), workers who are
hired for such tasks are often low-status and low-wage, isolated, and
asked to keep what they've seen in secret under restrictive NDAs.
Screening through the reported user-generated content is connected with
exposure to violent and deeply disturbing materials, with child
pornography, murders, or suicides as examples of the most extreme cases.
This can lead to serious psychological damage, like depression, or PTSD
(Roberts (2014)). Some of the employees filed a lawsuit against Facebook
and as a result, the company agreed to pay \$52M in compensation for
mental health issues developed during the job
(\url{https://www.theverge.com/2020/5/12/21255870/facebook-content-moderator-settlement-scola-ptsd-mental-health}).
Taking into consideration that Facebook employs 15K moderators
(\url{https://www.forbes.com/sites/johnkoetsier/2020/06/09/300000-facebook-content-moderation-mistakes-daily-report-says/?sh=6c6bdbbc54d0})
and most likely more are needed to keep up with the growing amount of
content, with the parallel considerations about the negative effects of
content moderation on mental health, a collaboration between humans and
machines in this area seems inevitable.

@@

There are different approaches when it comes to the moderation of online
content. One can follow the workflow of reactive moderation, which
happens once the content is published. Harmful messages can be either
reported by the users of the platforms or automated methods and then
sent for review to moderators. A set of actions can be then taken
depending on the platform and their community guidelines - on the
content or user level. A harmful message can be deleted, made invisible
to other users, or certain profanities can be altered with special signs
to censor them. Depending on the type and amount of infraction, a
particular user can be warned, muted or shadowbanned, or banned from
further participation in the community for a period of time. The
weakness of the reactive method is that the damage is done. Whoever is
the recipient of the abusive message has the chance to see it and
potentially suffer (Hoff \& Mitchell (2009), Keipi, Näsi, Oksanen, \&
Räsänen (2016), Wwachs2019associations). Yet another weakness connected
with relying solely on human reports is the content that is harmful but
unreported by a receipted or any bystander. Although the exact scale of
unreported content is not known, various self-report studies show that a
lot of children, teens, or even adults do not report cyberbullying or
harassment online (LINKS:
\url{https://www.ctvnews.ca/canada/as-the-pandemic-forces-us-online-lgbtq2s-teens-deal-with-cyberbullying-1.5430945}
; \url{https://www.adl.org/free-to-play-2020} ;
\url{https://www.ditchthelabel.org/wp-content/uploads/2017/05/InGameAbuse.pdf}).

@@

Pro-active moderation can be utilized using AI or other methods to
promote socially positive engagement. Instead of or in the combination
with punitive solutions like privileges restriction, one can induce
empathy or community norms with counter-speech. Counter speech as
described by Dangerous Speech Project
(\url{https://dangerousspeech.org/counterspeech/}) is ``any direct
response to hateful or harmful speech which seeks to undermine it.'' As
examined by Munger (2017), counter-speech can be effective in the
reduction of racist tweets (although only in the condition in which a
white male with high followers was approaching another white male). In a
study conducted by Bilewicz et al. (2021), a bot disguised as a Reddit
user, equipped with normative and empathetic interventions,
significantly decreased the amount of personal attacks generated on
Reddit. In yet another study by Miškolci, Kováčová, \& Rigová (2020),
this technique was not effective in changing the behavior of the users
(counter-speech here aimed at reducing the prejudice against Roma
minority in Slovakia), but encouraged bystanders to express pro-Roma
comments on specific Facebook posts. Counter-speech also has been shown
to have the potential to increase civility online in studies conducted
by Friess, Ziegele, \& Heinbach (2021), Molina \& Jennings (2018), Han,
Brazeal, \& Pennington (2018). \ldots{}

@@

This was a 6-months field experiment in a digital setting conducted on a
popular Q\&A and news forum, Reddit (www.reddit.com). We formed
treatment and control groups based on three main criteria: 1. During the
intervention period, we have expected to have 20 active volunteers at
any given time, each willing to conduct 10 interventions daily. Thus, we
needed approximately 200 attacks daily generated by the treatment
groups. 2. Recruitment of users who regularly attack others was
necessary to measure the effect of interventions at the end. 3.
Recruitment of users who were active during the whole preliminary
monitoring period was necessary to minimize the risk of attrition during
the study. First, we spent 9 weeks for preliminary Reddit's monitoring
period to recruit only those users who generate at least one personal
attack per week and were active during the whole period of the
monitoring. As mentioned, sustained activity was crucial to minimize the
risk users becoming inactive during the course of the study. Next, we
have calculated the daily average number of personal attacks generated
by the group who met the above criteria (which resulted in 357 attacks
per day - 1.94 attacks daily per person on average). Knowing that we
need around 200 attacks daily (just enough so our volunteers can keep up
with the volume) we have randomly selected 390 people for our study
groups (195 per group). The rest (304 people) were selected as our
control group.

Three groups were formed - two treatment groups (195 people in each) and
one control group (304 people). The first treatment group received
counter-speech interventions based on normative influence, while the
second one received interventions based on empathetic influence. Users
in the control group did not receive any intervention.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-barlett2021comparing}{}%
Barlett, C. P., Simmers, M. M., Roth, B., \& Gentile, D. (2021).
Comparing cyberbullying prevalence and process before and during the
COVID-19 pandemic. \emph{The Journal of Social Psychology}, 1--11.

@@

@@

@@

@@

@@

@@

>>>>

Although much effort has been made in order to tackle the problem of
verbal aggression and harassment online, looking at various reports and
surveys \todo{refs}, it remains a common hindrance for people engaging
with social media in their everyday lives. The problem got exacerbated
in the midst of the COVID19 pandemic \todo{is it less coloquial now?},
during which a majority of our social life moved to cyberspace. During
this shift, there was an increase in cyberbullying attitudes and
perpetration (Barlett, Simmers, Roth, \& Gentile (2021)), 90\% increase
in public reports of illegal online content Grant (2021), including
114\% increase in non-consensual sharing of intimate images, 30\%
increase in cyberbullying, as well as 40\% of increase in adults
reporting online
harassment.\footnote{The increase is reported as a relative change between the year 2019 and 2020.}
According to a report conducted by company L1ght (L1ght, 2020), hate
speech directed towards China and the Chinese went up by 900\% on
Twitter. Gaming platforms were in the spotlight as well, with a 40\%
increase in toxicity on Discord
\footnote{In this industry report, the increase is reported as a relative change between the year 2019 and 2020 as well, with no absolute indicators.}.

But alongside the growing need for even more efficient and proactive
moderation, the capacity to execute it did not go hand in hand, forcing
companies and policymakers to rethink the current model of moderation
processes and workforce. Due to the COVID19 restrictions including
social distancing, a lot of those serving the role of moderators had to
be sent home (Bhattacharya, 2021) without the ability to work remotely
because of the constraints affiliated with restrictive non-disclosure
agreements (NDA) among others. Curtailing the moderators' workforce was
accompanied by more agency given to algorithms and AI-based moderation.
Those changes, as argued by Gerrard (2020), can be seen as a serious red
flag in terms of safety for all users on online platforms.

@@

The hindrances and threats that go along with the Artificial
Intelligence-based methods for moderation have been widely debated, with
the most critical discussions revolving around technology performance
(MacAvaney et al., 2019; Schmidt \& Wiegand, 2017). State-of-the-art
solutions are mostly governed by statistical methods including deep
learning and machine learning (Jordan \& Mitchell, 2015; LeCun, Bengio,
\& Hinton, 2015; Sejnowski, 2020). Their performance is inherently tied
to the amount of data being fed to the system and the quality of its
annotation. \todo{This deserves a developed paragraph with examples}At
different stages of the process, from data gathering and preparation,
annotation to the training or algorithms themselves, biases seem to be
omnipresent Mehrabi, Morstatter, Saxena, Lerman, \& Galstyan (2021).

\todo{This deserves a developed paragraph with examples}Users' of online
services are also creative in their strategies to circumvent automated
content moderation systems and as shown by Gröndahl, Pajola, Juuti,
Conti, \& Asokan (2018), current techniques are vulnerable to the most
common evasion attacks like word changes (inseting typos and leetspeak),
word-boundary changes (inserting or removing whitespace), or word
appending (appending common or non-hateful words like ``love'').

\todo{This deserves a developed paragraph with examples}Lack of
generalisability of the models---an ability to perform well on datasets
coming from sources other than the one used for training is a serious
shortcoming as well (Rosa et al., 2019; Swamy, Jamatia, \& Gambäck,
2019; Yin \& Zubiaga, 2021). As shown by Wu, Ribeiro, Heer, \& Weld
(2019), Lipton \& Steinhardt (2019), and Musgrave, Belongie, \& Lim
(2020) in practice, the development of such models often lacks thorough
error analysis and legitimate experimental methodology, which can result
in non-reproducibility. This is also connected with a potential lack of
thorough understanding of the limitations of the models and spurious
conclusions being made to a wider public. Specifically, @Lipton \&
Steinhardt (2019) distinguishes four dysfunctional patterns occurring in
the current research paradigm in the industry and academia alike. First,
the inability to draw a clear distinction between speculation and
explanation, with the first one often being disguised as the
second\todo{give an example}. Second, the inability of successful
identification of the sources of performance improvement (whether it was
problem formulation, optimization of the heuristics, data-preprocessing,
hyperparameter tuning, or perhaps yet another
aspect)\todo{give an example}. Third, ``mathiness''---the use of obscure
language and often covering weak argumentation with the alluring but
often apparent depth of technical jargon\todo{Give an example}. Last but
not least---misuse of language\todo{Give an example}. This includes
suggestive definitions without proper explanation of what they mean in
the context (e.g.~inflating good performance in simple NLP tasks to
human-level understanding), overloading the papers with technical
terminology, or suitcase words (words that can encompass a variety of
meanings, e.g.~consciousness).

Yet another obstacle in the process is the lack of gold standard in
dataset creation and taxonomies of abusive language being used for
instance in the process of annotating different datasets. Frequently
people obtain data from various sources and do not follow any
universally used instructions when it comes to annotation, leading to
discrepancies between various datasets being tagged within one domain
(e.g.~hate speech). Lack of expert annotators and proper annotation
criteria and instructions are also widespread, with the common practice
of hiring untrained workers from Mechanical Turk or other crowdsourcing
platforms.

Although there are some initiatives developed in response, most notably,
functional tests for Hate Speech Detection Models created by Röttger et
al. (2020), or the Online Safety Data Initiative (OSDI) (\emph{About the
Online Safety Data Initiative}, n.d.), focused on projects related to
improving access to data, standardizing the description of online harms,
as well as creating tools and benchmarks for evaluation of technologies
focused on safety, much effort must be made before wider adoption of
such solutions comes into force.

At the same time, only automated methods can scan through the massive
amount of content being generated every day on different platforms. On
Facebook, there are more than 3B comments and likes daily
({``Facebook,''} 2012), 500M tweets are sent daily on Twitter (\emph{10
{Twitter} {Statistics} {Every} {Marketer} {Should} {Know} in 2021
{[}{Infographic}{]}}, 2021), and over 2B comments made by users of
Reddit in 2020 ({``Reddit in 2020,''} 2020) which is almost 3M comments
made daily. With this amount of content, it's either impossible or
extremely costly to scale the moderation workforce. One can also have
doubts about the ethical aspects of hiring workers who are often unaware
of how this kind of task will affect their well-being. Being submersed
in the cyber-Augean stables takes a toll on many---as examined by
Roberts (2014) \& Roberts (2016). Workers hired for such tasks are often
low-status and low-wage, isolated and asked to keep what they've seen in
secret under restrictive NDAs. This in turn makes the research in the
area extremely difficult, since moderators are not allowed to talk about
their work conditions or any other related subject. Those who decided to
break the NDA are risking a penalty. Screening through the reported
user-generated content is connected with exposure to violent and deeply
disturbing materials, with child pornography, murders, or suicides as
examples of the most extreme cases. This can lead to serious
psychological damage, such as depression, or PTSD (Roberts, 2014). Some
of the employees filed a lawsuit against Facebook and as a result, the
company agreed to pay \$52M in compensation for mental health issues
developed during the job (Newton, 2020). Taking into consideration that
Facebook employs 15K moderators (Koetsier, 2020) and most likely more
are needed to keep up with the growing amount of content, with the
parallel considerations about the negative effects of content moderation
on mental health, a collaboration between humans and machines in this
area seems inevitable.

@@

There are different approaches when it comes to the moderation of online
content. One can follow the workflow of reactive moderation, which
happens once the content is published. Harmful messages can be either
reported by the users of the platforms or automated methods and then
sent for review to moderators. A set of actions can be then taken
depending on the platform and their community guidelines---on the
content or user level. A harmful message can be deleted, made invisible
to other users, or certain profanities can be altered with special signs
to censor them. Depending on the type and amount of infraction, a
particular user can be warned, muted or shadowbanned, or banned from
further participation in the community for a period of time. The
weakness of the reactive method is that the damage is done. Whoever is
the recipient of the abusive message has the chance to see it and
potentially suffer Wachs et al. (2019). Yet another weakness connected
with relying solely on human reports is the content that is harmful but
unreported by a receipted or any bystander. Although the exact scale of
unreported content is not known, various self-report studies show that a
lot of children, teens, or even adults do not report cyberbullying or
harassment online ({``Free to {Play}?''} 2020; French, 2021; {``In,''}
2017).

@@

Pro-active moderation can be utilized using AI or other methods to
promote socially positive engagement. Instead of or in the combination
with punitive solutions such as privileges restriction, one can induce
empathy or community norms with counter-speech. Counter speech as
described by Dangerous Speech Project ({``Counterspeech {{}} {Dangerous}
{Speech} {Project},''} 2017) is ``any direct response to hateful or
harmful speech which seeks to undermine it.'' As examined by Munger
(2017), counter-speech can be effective in the reduction of racist
tweets (although only in the condition in which a white male with high
followers was approaching another white male). In a study conducted by
Bilewicz et al. (2021), a bot disguised as a Reddit user, equipped with
normative and empathetic interventions, significantly decreased the
amount of personal attacks generated on Reddit. In yet another study by
Miškolci, Kováčová, \& Rigová (2020), this technique was not effective
in changing the behavior of the users (counter-speech here aimed at
reducing the prejudice against Roma minority in Slovakia), but
encouraged bystanders to express pro-Roma comments on specific Facebook
posts. Counter-speech also has been shown to have the potential to
increase civility online in studies conducted by Friess, Ziegele, \&
Heinbach (2021), Molina \& Jennings (2018), Han, Brazeal, \& Pennington
(2018). \ldots{}

@@

This was a 6-months field experiment in a digital setting conducted on a
popular Q\&A and news forum, Reddit (www.reddit.com). We formed
treatment and control groups based on three main criteria: 1. During the
intervention period, we have expected to have 20 active volunteers at
any given time, each willing to conduct 10 interventions daily. Thus, we
needed approximately 200 attacks daily generated by the treatment
groups. 2. Identification of users who regularly attack others was
necessary to measure the effect of interventions at the end. 3.
Identification of users who were active during the whole preliminary
monitoring period was necessary to minimize the risk of attrition during
the study. First, we spent 9 weeks for preliminary monitoring period to
recruit only those users who generate at least one personal attack per
week and were active during the whole period of the monitoring. As
mentioned, sustained activity was crucial to minimize the risk of users
becoming inactive during the course of the study. Next, we calculated
the daily average number of personal attacks generated by the group who
met the above criteria (which resulted in 357 attacks per day, 1.94
attacks daily per person on average). Knowing that we need around 200
attacks daily (just enough so our volunteers can keep up with the
volume) we have randomly selected 390 people for our study groups (195
per intervention type). The rest (304 people) were selected as our
control group. The first treatment group received normative
counter-speech interventions, while the second one received empathetic
interventions. Users in the control group did not receive any
intervention.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-noauthor_10_2021}{}%
\emph{10 {Twitter} {Statistics} {Every} {Marketer} {Should} {Know} in
2021 {[}{Infographic}{]}}. (2021). Retrieved from
\url{https://www.oberlo.com/blog/twitter-statistics}

\leavevmode\hypertarget{ref-onlinesafetydata}{}%
\emph{About the online safety data initiative}. (n.d.).

\leavevmode\hypertarget{ref-barlett2021comparing}{}%
Barlett, C. P., Simmers, M. M., Roth, B., \& Gentile, D. (2021).
Comparing cyberbullying prevalence and process before and during the
COVID-19 pandemic. \emph{The Journal of Social Psychology}, 1--11.

\leavevmode\hypertarget{ref-bhattacharya}{}%
Bhattacharya, A. (2021). How {Covid}-19 lockdowns weakened {Facebook}'s
content moderation algorithms. Retrieved from
\url{https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}

@@

\leavevmode\hypertarget{ref-noauthor_counterspeech_2017}{}%
Counterspeech {{}} {Dangerous} {Speech} {Project}. (2017). Retrieved
from \url{https://dangerousspeech.org/counterspeech/}

\leavevmode\hypertarget{ref-noauthor_facebook:_2012}{}%
Facebook: 3.2 {Billion} {Likes} \& {Comments} {Every} {Day}. (2012).
Retrieved from
\url{https://martech.org/facebook-3-2-billion-likes-comments-every-day/}

\leavevmode\hypertarget{ref-noauthor_free_nodate}{}%
Free to {Play}? {Hate}, {Harassment} and {Positive} {Social}
{Experience} in {Online} {Games} 2020. (2020). Retrieved from
\url{https://www.adl.org/free-to-play-2020}

\leavevmode\hypertarget{ref-french_as_2021}{}%
French, C. (2021). As the pandemic forces us online, {LGBTQ2S}+ teens
deal with cyberbullying. Retrieved from
\url{https://www.ctvnews.ca/canada/as-the-pandemic-forces-us-online-lgbtq2s-teens-deal-with-cyberbullying-1.5430945}

@@

\leavevmode\hypertarget{ref-grant_2021}{}%
Grant, J. (2021). Australia's eSafety commissioner targets abuse online
as covid-19 supercharges cyberbullying \textbar{} the strategist.
Retrieved from
\url{https://www.aspistrategist.org.au/australias-esafety-commissioner-targets-abuse-online-as-covid-19-supercharges-cyberbullying/}

@@

\leavevmode\hypertarget{ref-noauthor_:game_nodate}{}%
In:{Game} {Abuse}. (2017). Retrieved from
\url{https://www.ditchthelabel.org/research-papers/ingame-abuse/}

@@

\leavevmode\hypertarget{ref-koetsier_report}{}%
Koetsier, J. (2020). Report: {Facebook} {Makes} 300,000 {Content}
{Moderation} {Mistakes} {Every} {Day}. Retrieved from
\url{https://www.forbes.com/sites/johnkoetsier/2020/06/09/300000-facebook-content-moderation-mistakes-daily-report-says/}

\leavevmode\hypertarget{ref-noauthor_l1ght_2020}{}%
L1ght. (2020). L1ght releases groundbreaking report on corona-related
hate speech and online toxicity. Retrieved from
\url{https://l1ght.com/l1ght-releases-groundbreaking-report-on-corona-related-hate-speech-and-online-toxicity/}

@@

\leavevmode\hypertarget{ref-newton_facebook_2020}{}%
Newton, C. (2020). Facebook will pay \$52 million in settlement with
moderators who developed {PTSD} on the job. Retrieved from
\url{https://www.theverge.com/2020/5/12/21255870/facebook-content-moderator-settlement-scola-ptsd-mental-health}

\leavevmode\hypertarget{ref-noauthor_reddit_nodate}{}%
Reddit in 2020. (2020). Retrieved from
\url{https://www.reddit.com/r/blog/comments/k967mm/reddit_in_2020/}

@@

\leavevmode\hypertarget{ref-wachs2019associations}{}%
Wachs, S., Wright, M. F., Sittichai, R., Singh, R., Biswal, R., Kim, E.,
\ldots{} others. (2019). Associations between witnessing and
perpetrating online hate in eight countries: The buffering effects of
problem-focused coping. \emph{International Journal of Environmental
Research and Public Health}, \emph{16}(20), 3992.
